---
title: "PA2_RepRes"
author: "Edoardo Bompiani"
date: "22/10/2015"
output: html_document
keep_md: true
---


The following libraries will be used in the analysis 

```{r, echo=TRUE}
library(plyr)
library(ggplot2)
library(RCurl)
```

* **plyr**: used to manipulate datas
* **ggplot2**: used for some of the plot
* **RCurl**: used to get file in https

I will suppose that the required project has been cloned in the home 
directory of a linux machine; otherwise the proper working directory should be inserted below

```{r, echo=TRUE}
setwd("~/RepData_PeerAssessment2")
```

## Loading and preprocessing the data
If they are not locally stored I download the required files: 

* the data file: https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2
* the documentation file: https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2Fpd01016005curr.pdf
* the FAQ file: https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2FNCDC%20Storm%20Events-FAQ%20Page.pdf

```{r, echo=TRUE}
destfile="StormData.csv.bz2"
fileURL="https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
if(!file.exists(destfile)){
    download.file(url=fileURL,
              destfile=destfile,
              method='curl') 
}

destfile="01016005curr.pdf"
fileURL="https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2Fpd01016005curr.pdf"
if(!file.exists(destfile)){
    download.file(url=fileURL,
              destfile=destfile,
              method='curl') 
}

destfile="FAQ_Page.pdf"
fileURL="https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2FNCDC%20Storm%20Events-FAQ%20Page.pdf"
if(!file.exists(destfile)){
    download.file(url=fileURL,
              destfile=destfile,
              method='curl') 
}
```

